\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-25 paper.tex

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{BATE}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} (BA) provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{BATE}$ is able to maximize revenue when network fails.
%$\mathsf{BATE}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{BATE}$ over inter-DC WAN.
The three core components of  $\mathsf{BATE}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{BATE}$ can speed up the online admission control by 30 $\times$ at the expense of only a 5\% higher rejection ratio. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{BATE}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{BATE}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Thirdly, 
we implement $\mathsf{BATE}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{BATE}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{BATE}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of a rejection ratio that is only 5\% higher than the optimal strategy;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{BATE}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under BATE, links can maintain high utilization.

@@

\textbf{Network failure scenario model:} 
%$\mathsf{BATE}$ relies on network operators to provide link failure probabilities.
%A series of failure events (e.g., power outage, configuration mistakes, firmware bugs) directly lead to link failures.
%%According to the report of Google \cite{evole}, more than 90\% of the failure events can lead to high packets losses, or blackholes to entire data centers and they might occur anytime.
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
%For each link $e$, operators can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1min).
%The link up probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
%Inspired by the site reliability engineering (SRE) technology\cite{jointfailure,overview}, we propose a general failure model.
The inter-DC WAN is modeled as a directed graph $G(V,E)$, where the set of nodes $V$ represent the data centers, 
and the set of links $E$ represent directed links between them. 
A network scenario $\mathbf{z}=\{\mathbf{z}_1,\mathbf{z}_2,...,\mathbf{z}_{|E|}\}$ is a vector of link states, 
where each element $\mathbf{z}_i \in \{0,1\}$ denotes whether the $i$-th link is up ($\mathbf{z}_i=1$) or down ($\mathbf{z}_i=0$). 
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
We assume network operators can use historical data to estimate the failure probability $x_i$ for this link, which are statistically indenpendent. 
%can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1 min).
%probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
Let $Z$ denote the network scenario set, %and $p_{\mathbf{z}}$ is the probability that a scenario $\mathbf{z}\in Z$ may happen.
%Each link is up with the probability of $p_i$. \cite{Teavar}
%Let $z_i'$ denote the value of $z_i$, and assume link failures are independent.
then the expected probability that a network scenario  $\mathbf{z} \in Z$ will happen is given by \cite{Teavar} 
\begin{eqnarray} \label{state}
%p_{\mathbf{z}}&=&p\left( z_1=z_1',z_2=z_2',z_3=z_3',...,z_{e}=z_{e}'\right)\nonumber \\
p_{\mathbf{z}}&=&\prod_{i=1}^{|E|}\big(\mathbf{z}_i \times (1-x_i)+ (1-\mathbf{z}_i) \times x_i\big)
\end{eqnarray}

@@

For an s-d pair $k$ of BA demand $d$, we use $R_{dk}^{\mathbf{z}}$ to denote the ratio of the effective bandwidth under network scenario $\mathbf{z}$ to the demanded bandwidth, which is defined as:
 \begin{eqnarray} \label{R2}
R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d}, \quad \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z.
\end{eqnarray}
%Figure \ref{Time-fig} gives an illustration on resource allocation return.
%For a given bandwidth allocation vector, it plots the sorted return and the corresponding probability.
%$R_{dk}^{\mathbf{z}}$ describes the allocation return under network scenario $\mathbf{z}$.
Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}, i.e., 
$\mathbf{z} \propto <d, \{f_d^t\}> \quad \Leftrightarrow \quad \forall k, R_{dk}^{\mathbf{z}} \ge 1$. 
%If for every source-destination pair $k$, the total reserved bandwidth through all available tunnels is larger than $\mathbf{b}^k_d$, then the bandwidth demand can still be satisfied, and network scenario $\mathbf{z}$ can be regarded as \textit{qualified}, i.e., 
%$R_{dk}^{\mathbf{z}} \ge 1, \forall k \in K$.
To meet the availability target, we should guarantee the total probability of the qualified scenarios 
is no less than the availability target, i.e., $\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_d$.
%for each s-d pair $k$ of demand $d$.
%$\forall d \in \hat{D}, k \in K$.
%This is a step function and we define the following potential function:
% 
%  \begin{eqnarray} \label{B3}
%\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_i, \forall d \in \hat{D}
%\end{eqnarray}
%$R_{dk}^{\mathbf{z}}$ is the ratio of allocated bandwidth to  demand over node pair $k$ under network scenario $\mathbf{z}$.
However, this condition will result in an mixed interger linear programming problem, 
and we choose to relax it and sovle the following linear programming problem.

@@

Besides, the bandwidth allocation result $f_{d}^t$ should be non-negative and limited by the network capacity, i.e.,
\begin{equation}
f_{d}^t \ge 0, \quad\forall d \in D ,  k\in K,   t\in T_{k}.
\label{constraint-f2}
\end{equation}
%Then total traffic through link $e$ should not be larger than its capacity $c_e$:
and
\begin{equation}
 \sum_{d \in \hat{D}}\ \sum_{k\in K, t\in T_{k}}f_{d}^tu_t^e \le c_e, \quad \forall e \in E.
\label{constraint-e2}
\end{equation}

@@

For a specific network scenario $ \mathbf{z}$ (where one link failure occurs) in consideration, 
%let
%$f^{\mathbf{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \mathbf{z}}_k$, where 
%$T^ { \mathbf{z}}_k$ denote the set of surviving tunnels for the s-d pair $k$ under scenario $ \mathbf{z}$.
the ratio of allocated bandwidth to a user's demanded bandwidth is \footnote{This is the same as equation (3), but we omit the superscript $\mathbf{z}$ of $R_{dk}^\mathbf{z}$.}

@@

\begin{equation}
r_d=
\begin{cases}
g_d &\text{if $R_{dk} \ge 1$ for every $k \in K$}\\
(1-\mu_{d})g_d &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation}

@@

\begin{equation}
\label{A-SSS2}
\begin{cases}
y_d \in \{0,1\} &{\forall d \in \hat{D}} \\
r_d  =  g_d \times \Big(y_d+(1-\mu_{d})\times (1-y_d)\Big) &{\forall d \in \hat{D}} \\
R_{dk} <  M\times y_d+1-y_d &{\forall d \in \hat{D},  k\in K} \\
R_{dk} \ge   y_d &{\forall d \in \hat{D},  k\in K}
\end{cases}
\end{equation}
where $M$ is a constant large enough (e.g., at least larger than the upper bound of $R_{dk}$).

@@

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of only 5\% higher rejection ratio, 
(ii) our pruning-augmented scheduling algorithm runs xx$\times$ faster with only 6\% waste of total bandwidth and 8\% loss in the overall availability, 
and (iii) our greedy failure recovery algorithm needs xx$\times$ less time to react, 
where the achieved profit decreases by less than 10\%.

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\textbf{Testbed setup}
We build a small testbed with 6 servers to emulate an inter-DC WAN connecting 6 DCs, as shown in Figure \ref{testbed}. 
The inter-DC links run at 1Gbps, and we add 100ms delay on each link to emulate a WAN environment.
Each server is equipped with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, 
and on each server we start 20 VMs, which are all connected to an Open vSwitch \cite{openvswitch}.
The VMs run CentOS 7 and use Linux v4.15.6 kernel \cite{Kermel} with our rate limiting module plugged in. 
%We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Every second, we emulate link failures by shutting down the corresponding VM interfaces 
under the failure probabilities shown in Fig. \ref{testbed}, 
and bring them online after 3 seconds. 
We also deploy our controller and brokers on extra VMs. 
The network agent module in each broker uses Floodlight \cite{floodlight} to control the vSwitch, 
while the latter monitors link status and reports any failure to the former.
If not stated otherwise, we use 4 shortest paths between each source-destination pair as the tunnels in TE algorithms.

@@

\textbf{A public cloud example}
We firstly evaluate a public cloud case.
Assume tenants arrive at the public cloud under poisson process with mean arrival rate 2 every minute and the duration of each bandwidth demand is under exponential distribution with a mean of 5 minutes.
Bandwidth demands between each node pair are under uniform distribution between 10Mbps and 50Mbps.
Every 1Mbps is sold 1$\$$.
%The profit of each tenant (i.e., $w_i$) is proportional to his/her total bandwidth demand.
Availability targets and refunding ratio are randomly chosen from Azure SLAs \cite{azure}.
Each experiment lasts 100 minutes and is repeated 20 times, where the error bars paints the maximal, minimal and mean value.

Figure \ref{e2}(a) demonstrates $\mathsf{BATE}$ only performs slightly worse than the optimal solution (about 4\%) and is at least 2 $\times$ better than the \textit{Fixed} admission control.
This is because $\mathsf{BATE}$ fully considers the availability diversity of tenants.
In contrast, \textit{Fixed} admission control can't change tenants' routing during runtime and such inflexibility leads to higher rejection rate. 
Figure \ref{e2}(b) shows once a tenant's demand is admitted, $\mathsf{BATE}$ can guarantee bandwidth.
FFC and TEAVAR with \textit{Fixed} admission control perform slightly better than when they are without admission control since many tenants' demands are rejected, but they also perform worse than $\mathsf{BATE}$, because FFC is too conservative and and TEAVAR ignores the diverse demands.
Figure \ref{e2}(c) shows $\mathsf{BATE}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.
This is because $\mathsf{BATE}$ pre-computes backup allocation with maximal profit and they can be put into practice as far as failures are detected.
We measure total bytes loss according to \textit{iperf} server side reports and packet counters in the switches, then finally derive the data loss ratio.
Figure \ref{e2}(d) demonstrates data loss ratio after network fails, where $\mathsf{BATE}$ performs about 8\% worse than FFC.
FFC performs best since it keeps network utilization low and almost no congestion occurs when network fails, 
while $\mathsf{BATE}$ focuses on Monetary gain rather than data loss.
%, where  FFC-1 and FFC-2 
%denote FFC with and without Fixed admission control,  respectively.
%where TEAVAR-1 and TEAVAR-2 are 
%denote TEAVAR with and without Fixed admission control, 
%We can see that 
%Specially, more than 85\% services achieve  95\% availability under $\mathsf{BATE}$, while only about 73\% and 60\%  services achieve this target under TEAVAR and FFC.
%Figure \ref{e2}(c) illustrates three schemes have similar performance for services with small availability target (i.e., $<95\%$).
%However, for services with large availability targets (i.e., $>=99\%)$,  $\mathsf{BATE}$ performs up to  20\% and 30\% better than TEAVAR and FFC.
%The reason for this is that $\mathsf{BATE}$ considers the diverse availability demands, so services with large targets can plunder
%bandwidth from others.
%Compared with TEAVAR, 20\% more applications satisfy their bandwidth demand with $\mathsf{BATE}$.
%Figure  \ref{e2}(c) shows the scheduled results with the same parameters.
%We can see the results approximate to that shown in Figure \ref{e2}(b).
%The gap is narrow, about 5\% on average.
%In the following evaluation, we develop a simulator to perform trace-driven simulations.
%Figure \ref{e2}(d) demonstrates the availability deviation between the testbed and simulation under the same parameters.
%We can see that the error is narrow, i.e., more than 90\% time the difference is less than 5\%.

>>>>

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{BATE}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} (BA) provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{BATE}$ is able to maximize revenue when network fails.
%$\mathsf{BATE}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{BATE}$ over inter-DC WAN.
The three core components of  $\mathsf{BATE}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{BATE}$ can speed up the online admission control by 30$\times$ at the expense of only a xx\% false rejections. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{BATE}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{BATE}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Thirdly, 
we implement $\mathsf{BATE}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{BATE}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{BATE}$ can 
(1) speed up the online admission control by 30$\times $ at the expense of a false rejection ratio that is only around xx\%;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{BATE}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under BATE, links can maintain high utilization.

@@

\textbf{Network failure scenario model:} 
%$\mathsf{BATE}$ relies on network operators to provide link failure probabilities.
%A series of failure events (e.g., power outage, configuration mistakes, firmware bugs) directly lead to link failures.
%%According to the report of Google \cite{evole}, more than 90\% of the failure events can lead to high packets losses, or blackholes to entire data centers and they might occur anytime.
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
%For each link $e$, operators can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1min).
%The link up probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
%Inspired by the site reliability engineering (SRE) technology\cite{jointfailure,overview}, we propose a general failure model.
The inter-DC WAN is modeled as a directed graph $G(V,E)$, where the set of nodes $V$ represent the data centers, 
and the set of links $E$ represent directed links between them. 
A network scenario $\mathbf{z}=\{\mathbf{z}_1,\mathbf{z}_2,...,\mathbf{z}_{|E|}\}$ is a vector of link states, 
where each element $\mathbf{z}_i \in \{0,1\}$ denotes whether the $i$-th link is up ($\mathbf{z}_i=1$) or down ($\mathbf{z}_i=0$). 
%Operators maintain the network empirical data, which can be used to estimate the link risks\cite{jointfailure,overview,evole}.
We assume network operators can use historical data to estimate the failure probability $x_i$ for this link, which are statistically indenpendent. 
%can examine historical data and track whether $e$ was up or down in a measured time epoch (e.g., 1 min).
%probability $p_i$ of link $i$ can be given by the up epoch percentage and its failure probability is $1-p_i$.
Let $Z$ denote the network scenario set, %and $p_{\mathbf{z}}$ is the probability that a scenario $\mathbf{z}\in Z$ may happen.
%Each link is up with the probability of $p_i$. \cite{Teavar}
%Let $z_i'$ denote the value of $z_i$, and assume link failures are independent.
then the expected probability that a network scenario  $\mathbf{z} \in Z$ will happen is given by \cite{Teavar} 
\begin{eqnarray*} \label{state}
%p_{\mathbf{z}}&=&p\left( z_1=z_1',z_2=z_2',z_3=z_3',...,z_{e}=z_{e}'\right)\nonumber \\
p_{\mathbf{z}}&=&\prod_{i=1}^{|E|}\big(\mathbf{z}_i \times (1-x_i)+ (1-\mathbf{z}_i) \times x_i\big)
\end{eqnarray*}

@@

For an s-d pair $k$ of BA demand $d$, we use $R_{dk}^{\mathbf{z}}$ to denote the ratio of the effective bandwidth under network scenario $\mathbf{z}$ to the demanded bandwidth, which is defined as:
 \begin{eqnarray} \label{R2}
R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d}, \quad \forall  d \in \hat{D}, k \in K, \mathbf{z}\in Z
\end{eqnarray}
%Figure \ref{Time-fig} gives an illustration on resource allocation return.
%For a given bandwidth allocation vector, it plots the sorted return and the corresponding probability.
%$R_{dk}^{\mathbf{z}}$ describes the allocation return under network scenario $\mathbf{z}$.
Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}, i.e., 
\[
\mathbf{z} \propto <d, \{f_d^t\}> \quad \Leftrightarrow \quad \forall k, R_{dk}^{\mathbf{z}} \ge 1
\] 
%If for every source-destination pair $k$, the total reserved bandwidth through all available tunnels is larger than $\mathbf{b}^k_d$, then the bandwidth demand can still be satisfied, and network scenario $\mathbf{z}$ can be regarded as \textit{qualified}, i.e., 
%$R_{dk}^{\mathbf{z}} \ge 1, \forall k \in K$.
To meet the availability target, we should guarantee the total probability of the qualified scenarios 
is no less than the availability target, i.e., $\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_d$.
%for each s-d pair $k$ of demand $d$.
%$\forall d \in \hat{D}, k \in K$.
%This is a step function and we define the following potential function:
% 
%  \begin{eqnarray} \label{B3}
%\sum_{R_{dk}^{\mathbf{z}} \ge 1} p_{\mathbf{z}} \ge \beta_i, \forall d \in \hat{D}
%\end{eqnarray}
%$R_{dk}^{\mathbf{z}}$ is the ratio of allocated bandwidth to  demand over node pair $k$ under network scenario $\mathbf{z}$.
However, this condition will result in an mixed interger linear programming problem, 
and we choose to relax it and sovle the following linear programming problem.

@@

Besides, the bandwidth allocation result $f_{d}^t$ should be non-negative and limited by the network capacity, i.e.,
\begin{equation}
f_{d}^t \ge 0, \quad\forall d \in D ,  k\in K,   t\in T_{k}
\label{constraint-f2}
\end{equation}
%Then total traffic through link $e$ should not be larger than its capacity $c_e$:
and
\begin{equation}
 \sum_{d \in \hat{D}}\ \sum_{k\in K, t\in T_{k}}f_{d}^tu_t^e \le c_e, \quad \forall e \in E
\label{constraint-e2}
\end{equation}

@@

For a specific network scenario $ \mathbf{z}$ (where one link failure occurs) in consideration, 
%let
%$f^{\mathbf{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \mathbf{z}}_k$, where 
%$T^ { \mathbf{z}}_k$ denote the set of surviving tunnels for the s-d pair $k$ under scenario $ \mathbf{z}$.
the ratio of allocated bandwidth to a user's demanded bandwidth is 
\footnote{This is the same as equation (\ref{R2}), but we omit the superscript $\mathbf{z}$ of $R_{dk}^\mathbf{z}$.}

@@

\begin{equation*}
r_d=
\begin{cases}
g_d &\text{if $R_{dk} \ge 1$ for every $k \in K$}\\
(1-\mu_{d})g_d &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation*}

@@

%\begin{equation}
%\label{A-SSS2}
%y_d \in \{0,1\} &{\forall d \in \hat{D}} \\
%r_d  =  g_d \times \Big(y_d+(1-\mu_{d})\times (1-y_d)\Big) &{\forall d \in \hat{D}} \\
%R_{dk} <  M\times y_d+1-y_d &{\forall d \in \hat{D},  k\in K} \\
%R_{dk} \ge   y_d &{\forall d \in \hat{D},  k\in K}
%\end{equation}

\iffalse
\begin{equation}
\label{A-SSS2}
\begin{split}
&y_d \in \{0,1\}, \quad  \forall d \in \hat{D}\\
&r_d  =  g_d \times \Big(y_d+(1-\mu_{d})\times (1-y_d)\Big), \quad {\forall d \in \hat{D}}\\
&R_{dk} <  M\times y_d+1-y_d ,\quad{\forall d \in \hat{D},  k\in K} \\
&R_{dk} \ge   y_d,\quad {\forall d \in \hat{D},  k\in K}
\end{split}
\end{equation}
\fi
\begin{equation}
\label{A-SSS2}
\begin{array}{rcll}
y_d &\in &\{0,1\} &{\forall d \in \hat{D}} \\
r_d & = & g_d \times \Big(y_d+(1-\mu_{d})\times (1-y_d)\Big) &{\forall d \in \hat{D}} \\
R_{dk}& < & M\times y_d+1-y_d &{\forall d \in \hat{D},  k\in K} \\
R_{dk}& \ge &  y_d, &{\forall d \in \hat{D},  k\in K}
\end{array}
\end{equation}
where $M$ is a constant large enough (e.g., at least larger than the upper bound of $R_{dk}$).

@@

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of only xx\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs xx$\times$ faster while wasting only 6\% total bandwidth and losing only 8\% overall availability, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by xx$\times$, 
where the profit loss is below 10\%.

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\textbf{Testbed setup}
We build a testbed with 6 servers to emulate a small inter-DC WAN connecting 6 DCs, as shown in Figure \ref{testbed}. 
The inter-DC links run at 1Gbps, and we add 100ms delay on each link to emulate a WAN environment.
Each server is equipped with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, 
and on each server we start 20 VMs, which are all connected to an Open vSwitch \cite{openvswitch}.
The VMs run CentOS 7 and use Linux v4.15.6 kernel \cite{Kermel} with our rate limiting module plugged in. 
%We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Every second, we emulate link failures by shutting down the corresponding VM interfaces 
under the failure probabilities shown in Fig. \ref{testbed}, 
and bring them online after 3 seconds. 
We also deploy our controller and brokers on extra VMs. 
The network agent module in each broker uses Floodlight \cite{floodlight} to control the vSwitch, 
while the latter monitors link status and reports any failure to the former.
If not stated otherwise, we use 4 shortest paths between each source-destination pair as the tunnels in TE algorithms.

@@

\textbf{User demands arrive continuously.}
We first conduct experiments where user demands are generated from models used 
in some latest inter-DC traffic scheduling algorithms \cite{Guaranteeings,Online-deadline}. 
For each source-destination pair, the arrival of user bandwidth demands follows a poisson process, 
and the demand duration follows an exponential distribution.  
The mean inter-arrival time we use is 2 miniutes, and the mean duration is 5 minutes. 
The demanded bandwidth is uniformly distributed between 10 Mbps and 50 Mbps.
The availability targets and refunding ratio are chosen from the Azure SLAs \cite{azure}, 
and we assume a unit price is charged for 1 Mbps. 
Each experiment lasts 100 minutes, where link failures occur probabilistically, 
and is repeated for 50 times.

%The profit of each tenant (i.e., $w_i$) is proportional to his/her total bandwidth demand.
%Each experiment lasts 100 minutes and is repeated 20 times, where the error bars paints the maximal, minimal and mean value.
\textit{Admission control.} We evaluate how demands can be correctly admitted by $\mathsf{BATE}$, 
comparing with both the optimal admission strategy, 
and a strategy that assumes a \textit{fixed} bandwith allocation for demands that have already been admitted, which is effectively step (1) in $\mathsf{BATE}$.
Figure \ref{e2}(a) demonstrates that $\mathsf{BATE}$ performs closely to the optimal strategy, 
i.e., the false rejection ratio is at most 1\%, while the \textit{fixed} algorithm 
rejects least 10$\times$ more admissible demands. 
%This is because $\mathsf{BATE}$ fully considers the availability diversity of tenants.
%In contrast, \textit{Fixed} admission control can't change tenants' routing during runtime and such inflexibility leads to higher rejection rate. 
\textit{Traffic scheduling.} We evaluate, once a user demand is admitted, 
how often its bandwith availability requirement can be guaranteed. 
Since we emulate different link failures according to their probabilities in every second, 
we can measure how the bandwidth a user actually uses deviates from its requirement. 
If such a deviation is less than 1\%, we regard the bandwidth availability as \textit{satisfied in that second}. Figure \ref{e2}(b) shows the overall fraction of satisfication, under 
different levels of availability requirements (i.e., 95\%, 99\% and 99.99\%). 
We note that, FFC-fixed (or TEAVAR-fixed) in the figure represents applying FFC (or TEAVAR) 
only to demands admitted by the fixed admission control strategy, 
where the total bandwidth required for the admitted demands will be much lower. 
$\mathsf{BATE}$ always achieves the highest availability, even compared with FFC-fixed and TEAVAR-fixed. 
In particular, it has a clear advantage for high availability requirements (e.g., >99.99\%). 
To further illustrate the difference in their mechanisms, 
we plot in Figure \ref{e2}(c), for each algorithm, the ratio of the allocated bandwidth 
to the demanded bandwidth. 
The cdf curve shows that FFC is too conservative in bandwidth allocation, 
which failes to allocate proper bandwidth in almost 60\% time.   
On the other hand, although TEAVAR provides bandwidth fairly well, 
it ignores the diverse availability requirements of different users, 
and achieves a lower satisfication ratio than $\mathsf{BATE}$.

\textit{Failure Recovery} We evaluate when failures do occur and cause SLA violations, 
how profit loss can be mitigated by our failure recovery scheme.
Figure \ref{e2}(d) plots the overall profit $\mathsf{BATE}$, FFC and TEAVAR can achieve for admitted demands, under three different admission control strategies, i.e., fixed, AD (which is the strategy $\mathsf{BATE}$ uses) and optimal. 
\textbf{TBD: This is because $\mathsf{BATE}$ pre-computes backup allocation with maximal profit and they can be put into practice as far as failures are detected.}
Figure \ref{e2}(e) further depicts the fraction of profit loss caused by SLA violations, where the baseline for each algorithm is the profit it can achieve when no failures occur. 
\textbf{TBD: $\mathsf{BATE}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.}
Compared with TEAVAR, FFC has a lower profit loss ratio due to its conservative bandwidth allocation, as indicated in Figure \ref{e2}(c) earlier.
